---
title: "`circletabR`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{circletabR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
div.compare-brands {
  margin-bottom: 20px;
}

.compare-brands img {
  border: none;
}
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#| echo: false
library(circletabR)
```

The `circletabR` package currently provides a single function, `circletab` which can be used to produce a table where data values are represented as circles of varying size.  Consider the following data frame:

```{r, echo = FALSE}
set.seed(1234)

d <- data.frame(
  g1 = rep(c("Foo", "Bar", "Baz"), each = 3),
  g2 = rep(c("A", "B", "C"), 3), 
  value = runif(9)
)

knitr::kable(d, format = "markdown")
```

Data frames must contain 3 columns.  The first column will be used as row labels, and the second will be used as column labels.  Calling `circletab` produces the following:

```{r}
circletab(d, max_value = 1)
```
