---
title: "circletab"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{circletab}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
div.compare-brands {
  margin-bottom: 20px;
}

.compare-brands img {
  border: none;
}
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#| echo: false
library(circletab)
```

The `circletabR` package currently provides a single function, `circletab` which can be used to produce a table where data values are represented as circles of varying size.

Consider the following dataset, saved as `data_1`:

```{r}
#| echo: false
data_1 <- data.frame(
  brand = c("onenz", "skinny", "spark", "2degrees"),
  value = c(45, 49, 43, 54)
)

knitr::kable(data_1, format = "markdown")
```

We can display these scores as follows:

```{r}
#| echo: true
net_promoter_score(
  title = "Speed of resolution",
  description = paste(c(
    "Measures satisfaction as how quickly providers resolve customer service ",
    "issues (higher is better)."
  ), collapse = ""),
  data = data_1,
  unit = "%",
  range = c(0,100),
  bar_color = rgb(176, 12, 41, maxColorValue = 255),
  font_color = rgb(176, 12, 41, maxColorValue = 255)
)
```

Similarly, consider the following data, saved as `data_2`:

```{r}
#| echo: false
data_2 <- data.frame(
  brand = c(
    "contact", "mercury", "onenz", "skinny", "slingshot", "spark", "2degrees"
  ),
  value = c(-1, -11, -2, 11, 2, 2, 4)
)

knitr::kable(data_2, format = "markdown")
```

We can display these scores as follows:

```{r}
#| echo: true
net_promoter_score(
  title = "Net Promoter Score (NPS)",
  description = paste(c(
    "Mesaures how likely customers are to recommend their provider to friends ",
    "and family (higher is better)."
  ), collapse = ""),
  data = data_2,
  range = c(-20, 20),
  bar_color = rgb(63, 94, 88, maxColorValue = 255),
  font_color = rgb(63, 94, 88, maxColorValue = 255)
)
```
